|

### 2018-01-03 article/Funk-Mullen.Spine-of-Legal-Practice.Rmd
Revised figures

```{r code-to-code-network, fig.width=17.5, fig.height=12.5, fig.cap = "The structure of borrowings among nineteenth-century codes of civil procedure. Note that several versions of New York's Field Code were at the center of the network, while other states such as California and Ohio became centers of regional variations on the Field Code. States that adopted any of the variations on the Field Code became part of a network centered on New York capital."} 
set.seed(3728)
network_g <- ggraph(codes_g, "igraph", algorithm = "nicely") +
  geom_edge_fan(aes(edge_width = sections_borrowed, 
                    alpha = sections_borrowed),
                arrow = arrow(type = "closed", ends = "first",
                              length = unit(0.20, "inches"),
                               angle = 15)) +
  geom_node_point(aes(color = as.factor(distance)), size = 6) +   
  scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") +    
  scale_edge_alpha(range = c(0.5, 0.5), guide = "none") +   
  scale_color_manual(name = "Distance from a Field Code",
                     values = c("0" = "#ff0000",
                                "1" = "#1d91c0",
                                "2" = "#41b6c4",
                                "3" = "#7fcdbb",
                                "4" = "#c7e9b4",
                                "5" = "#edf8b1",
                                "6" = "#ffffd9",
                                "Inf" = "#dfc27d")) +
  ggforce::theme_no_axes() +  
  geom_node_text(aes(label = name), size = 5, family = "Palatino") +
  labs(title = "The migration of the Field Code",
       subtitle = "Codes of civil procedure connected by borrowed sections") +
  theme(legend.position = "bottom",
        panel.border = element_blank(),
        text = element_text(family = "Palatino"),
        legend.title = element_text(size = 18),
        legend.text = element_text(size = 15),
        plot.title = element_text(size = 22, face = "bold"),
        plot.subtitle = element_text(size = 18))
print(network_g)
ggsave("../out/figures/figure-05.svg", network_g, width = 17.5, height = 12.25)
ggsave("../out/figures/figure-05.pdf", network_g, width = 17.5, height = 12.25)
ggsave("../out/figures/figure-05.png", network_g, width = 17.5, height = 12.25)
```

@@

```{r CA1850-borrowings, fig.height=3, fig.align="center"}
spec_CA1850 <- spectrogram("CA1850", best_matches, 
                           white_list = c("LA1844", "NY1829", "NY1849", "NY1848"),
                           base_size = 10)
spec_CA1850_bw <- spectrogram("CA1850", best_matches, 
                              white_list = c("LA1844", "NY1829", "NY1849", "NY1848"),
                              base_size = 10, bw = TRUE)
if (!bw) {
  print(spec_CA1850) 
} else {
  print(spec_CA1850_bw)
} 
ggsave("../out/figures/figure-06.svg", spec_CA1850, width = 7, height = 3)
ggsave("../out/figures/figure-06.pdf", spec_CA1850, width = 7, height = 3)
ggsave("../out/figures/figure-06.png", spec_CA1850, width = 7, height = 3)
ggsave("../out/figures/figure-06-bw.svg", spec_CA1850_bw, width = 7, height = 3)
ggsave("../out/figures/figure-06-bw.pdf", spec_CA1850_bw, width = 7, height = 3)
ggsave("../out/figures/figure-06-bw.png", spec_CA1850_bw, width = 7, height = 3)
```

@@

```{r CA1851-borrowings, fig.height=3.5, fig.align="center"}
spec_CA1851 <- spectrogram("CA1851", best_matches, 
                           white_list = 3, base_size = 10)
spec_CA1851_bw <- spectrogram("CA1851", best_matches, 
                              white_list = 3, base_size = 10, bw = TRUE)
if (!bw) {
  print(spec_CA1851) 
} else {
  print(spec_CA1851_bw)
} 
ggsave("../out/figures/figure-07.svg", spec_CA1851, width = 7, height = 3.5)
ggsave("../out/figures/figure-07.pdf", spec_CA1851, width = 7, height = 3.5)
ggsave("../out/figures/figure-07.png", spec_CA1851, width = 7, height = 3.5)
ggsave("../out/figures/figure-07-bw.svg", spec_CA1851_bw, width = 7, height = 3.5)
ggsave("../out/figures/figure-07-bw.pdf", spec_CA1851_bw, width = 7, height = 3.5)
ggsave("../out/figures/figure-07-bw.png", spec_CA1851_bw, width = 7, height = 3.5)
```

@@

```{r WA1855-borrowings, fig.height=4.5, fig.align="center"}
spec_WA1855 <- spectrogram("WA1855", best_matches, 
                           white_list = c("CA1850", "CA1851", "IN1852", 
                                          "OR1854"),
                           base_size = 10)
spec_WA1855_bw <- spectrogram("WA1855", best_matches, 
                              white_list = c("CA1850", "CA1851", "IN1852", 
                                             "OR1854"),
                              base_size = 10, bw = TRUE)
if (!bw) {
  print(spec_WA1855) 
} else {
  print(spec_WA1855_bw)
} 
ggsave("../out/figures/figure-08.svg", spec_WA1855, width = 7, height = 4.5)
ggsave("../out/figures/figure-08.pdf", spec_WA1855, width = 7, height = 4.5)
ggsave("../out/figures/figure-08.png", spec_WA1855, width = 7, height = 4.5)
ggsave("../out/figures/figure-08-bw.svg", spec_WA1855_bw, width = 7, height = 4.5)
ggsave("../out/figures/figure-08-bw.pdf", spec_WA1855_bw, width = 7, height = 4.5)
ggsave("../out/figures/figure-08-bw.png", spec_WA1855_bw, width = 7, height = 4.5)
```

>>>>

```{r code-to-code-network, fig.width=17.5, fig.height=12.5, fig.cap = "The structure of borrowings among nineteenth-century codes of civil procedure. Note that several versions of New York's Field Code were at the center of the network, while other states such as California and Ohio became centers of regional variations on the Field Code. States that adopted any of the variations on the Field Code became part of a network centered on New York capital."} 
set.seed(3728)
network_g <- ggraph(codes_g, "igraph", algorithm = "nicely") +
  geom_edge_fan(aes(edge_width = sections_borrowed, 
                    alpha = sections_borrowed),
                arrow = arrow(type = "closed", ends = "first",
                              length = unit(0.20, "inches"),
                               angle = 15)) +
  geom_node_point(aes(color = as.factor(distance)), size = 6) +   
  scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") +    
  scale_edge_alpha(range = c(0.5, 0.5), guide = "none") +   
  scale_color_manual(name = "Distance from a Field Code",
                     values = c("Field code" = "#e41a1c",
                                "Original borrower" = "#377eb8",
                                "Subsequent borrower" = "#4daf4a",
                                "Independent" = "#984ea3"
                                # "3" = "#7fcdbb",
                                # "4" = "#c7e9b4",
                                # "5" = "#edf8b1",
                                # "6" = "#ffffd9",
                                # "Inf" = "#dfc27d"
                                )) +
  ggforce::theme_no_axes() +  
  geom_node_text(aes(label = name), size = 5, family = "Palatino") +
  labs(title = "The migration of the Field Code",
       subtitle = "Codes of civil procedure connected by borrowed sections") +
  theme(legend.position = "bottom",
        panel.border = element_blank(),
        text = element_text(family = "Palatino"),
        legend.title = element_text(size = 18),
        legend.text = element_text(size = 15),
        plot.title = element_text(size = 22, face = "bold"),
        plot.subtitle = element_text(size = 18))
print(network_g)
ggsave("../out/figures/figure-05.svg", network_g, width = 17.5, height = 12.25)
ggsave("../out/figures/figure-05.pdf", network_g, width = 17.5, height = 12.25)
ggsave("../out/figures/figure-05.png", network_g, width = 17.5, height = 12.25)
```

@@

```{r CA1850-borrowings, fig.height=3, fig.align="center"}
best_matches_combine_ny <- best_matches %>% 
  mutate(match_code = ifelse(match_code == "NY1848" | match_code == "NY1849",
                             "NY1848-49",
                             match_code))
spec_CA1850 <- spectrogram("CA1850", best_matches_combine_ny, 
                           white_list = c("LA1844", "NY1848-49"),
                           base_size = 10)
spec_CA1850_bw <- spectrogram("CA1850", best_matches_combine_ny, 
                              white_list = c("LA1844", "NY1848-49"),
                              base_size = 10, bw = TRUE)
if (!bw) {
  print(spec_CA1850) 
} else {
  print(spec_CA1850_bw)
} 
ggsave("../out/figures/figure-06.svg", spec_CA1850, width = 7, height = 3)
ggsave("../out/figures/figure-06.pdf", spec_CA1850, width = 7, height = 3)
ggsave("../out/figures/figure-06.png", spec_CA1850, width = 7, height = 3)
ggsave("../out/figures/figure-06-bw.svg", spec_CA1850_bw, width = 7, height = 3)
ggsave("../out/figures/figure-06-bw.pdf", spec_CA1850_bw, width = 7, height = 3)
ggsave("../out/figures/figure-06-bw.png", spec_CA1850_bw, width = 7, height = 3)
```

@@

```{r CA1851-borrowings, fig.height=3.5, fig.align="center"}
best_matches_ca1851 <- best_matches %>% 
    mutate(match_code = ifelse(match_code == "NY1848" | match_code == "NY1849" | match_code == "NY1850",
                             "NY1848-50",
                             match_code))
spec_CA1851 <- spectrogram("CA1851", best_matches_ca1851, 
                           white_list = 3, base_size = 10)
spec_CA1851_bw <- spectrogram("CA1851", best_matches_ca1851, 
                              white_list = 3, base_size = 10, bw = TRUE)
if (!bw) {
  print(spec_CA1851) 
} else {
  print(spec_CA1851_bw)
} 
ggsave("../out/figures/figure-07.svg", spec_CA1851, width = 7, height = 3.5)
ggsave("../out/figures/figure-07.pdf", spec_CA1851, width = 7, height = 3.5)
ggsave("../out/figures/figure-07.png", spec_CA1851, width = 7, height = 3.5)
ggsave("../out/figures/figure-07-bw.svg", spec_CA1851_bw, width = 7, height = 3.5)
ggsave("../out/figures/figure-07-bw.pdf", spec_CA1851_bw, width = 7, height = 3.5)
ggsave("../out/figures/figure-07-bw.png", spec_CA1851_bw, width = 7, height = 3.5)
```

@@

```{r WA1855-borrowings, fig.height=4.5, fig.align="center"}
best_matches_wa1855 <- best_matches %>% 
  mutate(match_code = ifelse(match_code == "CA1850" | match_code == "CA1851",
                             "CA1850-51",
                             match_code))

spec_WA1855 <- spectrogram("WA1855", best_matches_wa1855, 
                           white_list = c("CA1850-51", "IN1852", 
                                          "OR1854"),
                           base_size = 10)
spec_WA1855_bw <- spectrogram("WA1855", best_matches_wa1855, 
                              white_list = c("CA1850-51", "IN1852", 
                                             "OR1854"),
                              base_size = 10, bw = TRUE)
if (!bw) {
  print(spec_WA1855) 
} else {
  print(spec_WA1855_bw)
} 
ggsave("../out/figures/figure-08.svg", spec_WA1855, width = 7, height = 4.5)
ggsave("../out/figures/figure-08.pdf", spec_WA1855, width = 7, height = 4.5)
ggsave("../out/figures/figure-08.png", spec_WA1855, width = 7, height = 4.5)
ggsave("../out/figures/figure-08-bw.svg", spec_WA1855_bw, width = 7, height = 4.5)
ggsave("../out/figures/figure-08-bw.pdf", spec_WA1855_bw, width = 7, height = 4.5)
ggsave("../out/figures/figure-08-bw.png", spec_WA1855_bw, width = 7, height = 4.5)
```
